Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-08-06 paper/current/main.tex
add ecsim

>>>>

\subsection*{Element-centric clustering similarity}
\js{
Element-centric clustering similarity \autocite{gates2019element} is unified similarity embracing disjoint, overlapping, and hierarchically structured clustering. Element-centric clustering similarity captures cluster-induces relationships between through cluster affiliation graph where one vertex set is the original element $V=\{v_1, ... v_N\}$ and the other corresponds to the cluster $C=\{c_1, ... c_M\}$ as a bipartite graph $\mathcal{B} (V \cup C, \mathcal{R})$. an undirected edge $a_{i\beta} \in \mathcal{R}$  denote element $v_i$ is a member of cluster $c_\beta$. For hierarchically structured clustering. each cluster $c_\beta$ is assigned a hierarchical level $l_{\beta} \in [0,1]$ by re-scaling the dendrogram according to the maximum path length from the roots. The weight of the cluster affiliation edge is given by the hierarchy weight function $a_{i\beta}  = e^{rl_{\beta}}$ with scaling parameter $r$ which determine the relative importance of membership at different levels of hierarchy. Here, lower $r$ focuses on the higher level of the hierarchy, and lower levels are treated as a refinement of the higher level. Larger $r$ emphasizes lower-level cluster structure, and higher levels of the hierarchy are seen as an aggregation of the lower-level structure. If $r=0$, every cluster is treated equally.

The cluster affiliation graph is projected onto  a cluster-induced element graph which is a weighted, directed graph summarizes the relationship induced by common cluster memberships. In the cluster-induced element graph,  each edge  between element $v_i$ and $v_j$ has weight $w_{ij} = \sum_{\gamma} \frac{a_{i\gamma}a_{j\gamma}}{\sum_{\kappa}a_{i\kappa} {\sum_{m}a_{m\gamma}}}$. Given a cluster-induces element graph with weighted matrix $W$, the personalized PageRank vector $p_i$  is used as membership-aware similarity between element $i$ and other elements in the graph. Then, the element-wise similarity of an element $v_i$ in two clustering  $\mathcal{A}$ and $\mathcal{B}$ is calculated with $S_i(\mathcal{A}, \mathcal{B}) = 1 - L_1(p_i^{\mathcal{A}},p_j^{\mathcal{B}})$, and the final elementric-centric similiarty of two clustering $\mathcal{A}$ and $\mathcal{B}$ is the average of the element-wise similarities, $S(\mathcal{A}, \mathcal{B}) =\frac{1}{N}\sum_{i=1}^{N} S_i(\mathcal{A}, \mathcal{B})$.}
